Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-12-11 src/tex/ms.tex
'Card' for cardinality isn't common notation

Under $H_1$, $Y$ also follows a binomial distribution, however it is conditioned by $n_{\lambda}=Card(\{F_\mathrm{NUV, i} \text{ if } F_\mathrm{NUV, i}>F_\mathrm{NUV, min}\}_{i \in [1,n]})$ the number of values of $F_\mathrm{NUV}$ in the experiment that exceed $F_\mathrm{NUV, min}$
\begin{equation}
\label{eq:semian:likelihoodH1}
P(Y=k|H_1) = \binom{n_{\lambda}}{k}f_\mathrm{life}^k(1-f_\mathrm{life})^{n_{\lambda}-k}.
\end{equation}

>>>>

Under $H_1$, $Y$ also follows a binomial distribution, however it is conditioned by $n_{\lambda} = n(\{F_\mathrm{NUV, i} \text{ if } F_\mathrm{NUV, i}>F_\mathrm{NUV, min}\}_{i \in [1,n]})$, the number of values of $F_\mathrm{NUV}$ in the experiment that exceed $F_\mathrm{NUV, min}$
\begin{equation}
\label{eq:semian:likelihoodH1}
P(Y=k|H_1) = \binom{n_{\lambda}}{k}f_\mathrm{life}^k(1-f_\mathrm{life})^{n_{\lambda}-k}.
\end{equation}
